Equivalent Income Outcome Visualisation

### 2023-08-30 minos/outcomes/equivalent_income_out.Rmd
Additions to the equivalent_income_out.Rmd

df <- combine_and_pivot_long(base.dat, 'Baseline', wage.dat, 'LivingWage', c('S7_housing_quality', 'income_boosted'))

outcomes.prep <- function(base.dat, int.dat, int.name, var) {
  boosted.pidps <- int.dat %>%
    filter(income_boosted == 'True') %>%
    select(pidp, time)

  df1 <- base.dat %>%
    select(pidp, time, all_of(var), weight) %>%

}

combine_and_pivot_long <- function(df1, df1.name, df2, df2.name, var) {
  # get only the columns we want a rename
  df1 <- df1 %>%
    select('pidp', 'time', all_of(var)) %>%
    set_names(c('pidp', 'time', df1.name))
  df2 <- df2 %>%
    select('pidp', 'time', all_of(var)) %>%
    set_names(c('pidp', 'time', df2.name))
  # merge on pidp and time
  merged <- merge(df1, df2, by = c('pidp', 'time'), all=TRUE)
  pivoted <- pivot_longer(data = merged,
                          cols = df1.name:df2.name,
                          names_to = 'scenario',
                          values_to = var)
  return(pivoted)
}

>>>>

# df <- combine_and_pivot_long(base.dat, 'Baseline', wage.dat, 'LivingWage', c('S7_housing_quality', 'income_boosted'))
# 
# outcomes.prep <- function(base.dat, int.dat, int.name, var) {
#   boosted.pidps <- int.dat %>%
#     filter(income_boosted == 'True') %>%
#     select(pidp, time)
#   
#   df1 <- base.dat %>%
#     select(pidp, time, all_of(var), weight) %>%
#     
# }
# 
# 
# 
# 
# combine_and_pivot_long <- function(df1, df1.name, df2, df2.name, var) {
#   # get only the columns we want a rename
#   df1 <- df1 %>%
#     select('pidp', 'time', all_of(var)) %>%
#     set_names(c('pidp', 'time', df1.name))
#   df2 <- df2 %>%
#     select('pidp', 'time', all_of(var)) %>%
#     set_names(c('pidp', 'time', df2.name))
#   # merge on pidp and time
#   merged <- merge(df1, df2, by = c('pidp', 'time'), all=TRUE)
#   pivoted <- pivot_longer(data = merged,
#                           cols = df1.name:df2.name,
#                           names_to = 'scenario',
#                           values_to = var)
#   return(pivoted)
# }
